Classifying Protein Secondary Structures through Deep Network Learning

### 2013-12-18 docs/paper.tex
Paper first draft complete

@@

\subsection{Ensembles}
Our best deep network performs signifcantly worse than the baseline neural network, so a natural modification is to try using ensembles of networks.
Since deep networks require significant time complexity, we were unable to train an ensemble of deep networks.
However, we were able to train an ensemble of simple neural networks with one hidden layer.
An ensemble of three neural networks has an average accuracy of 61.65\%.
The best baseline neural network settings, as discussed in section \ref{subsec:bestbaseline},
produced an average accuracy of 59.51\%, which is two percentage points lower than the ensemble.
So, using an ensemble clearly improves the performance of the baseline network, and we hypothesize that deep networks would also benefit from this technique.

@@

\section{Future Work}
%TODO
Ensembles of autoencoders
Other things than sigmoid
- sparse autoencoder

\section{Conclusion}
%TODO

%TODO Create Abstract

@@

@@

\bibitem{uci}
   C.L. Blake and C.J. Merz,
   `` UCI repository of machine learning databases"
   \textbf{http://archive.ics.uci.edu/ml/datasets/}
   \textbf{Molecular+Biology+(Protein+}
   \textbf{Secondary+Structure)}

>>>>

\begin{abstract}
Classifying the secondary structures of proteins is a well-known problem in molecular biology.
Our goal is explore the potential of applying deep learning methods to this domain.
We performed an empirical evaluation of deep network parameters on a network of stacked autoencoders.
We found that our best performance of 53.2\% resulted from parameters of window size 13, 6 hidden layers, and 26 units per hidden layer.
Unfortunately, this underperforms as compared to other learning methods.
\end{abstract}

@@

\subsection{Ensembles}
Our best deep network performs signifcantly worse than the baseline neural network, so a natural modification is to try using ensembles of networks.
Since deep networks require significant time complexity, we were unable to train an ensemble of deep networks.
However, we were able to train an ensemble of simple neural networks with one hidden layer.
An ensemble of three neural networks has an average accuracy of 61.65\%.
The best baseline neural network settings, as discussed in section \ref{subsec:bestbaseline},
produced an average accuracy of 59.51\%, which is two percentage points lower than the ensemble.
So, using an ensemble clearly improves the performance of the baseline network, and we hypothesize that deep networks would also benefit from this technique, but leave it to future work.

@@

\section{Future Work}
We considered additional modifications to the basic algorithm that we were unable to test due to time constraints.
We would have liked to experiment with additional functions for our hidden and output units, rather than only using a sigmoid.
One interesting modification would be using a function that further encourages sparsity by using a penalty term \cite{ng}.

\section{Conclusion}
We explored a deep network's ability to classsify secondary structures in proteins.
We created a baseline of a standard single-hidden layer neural network for comparison.
We did a parameter tuning study, and found that the best parameters for the deep network were a window size of 13 and 6 hidden layers with 26 units per layer, resulting in a final accuracy of 53.2\%.
We found that our deep networks were unable to achieve the accuracy of a standard neural network.

@@

\bibitem{Ng}
Andrew Ng,
   `` CS294 Lecture notes: Sparse autoencoder"
   \textbf{www.stanford.edu/class/cs294a/}
   \textbf{sparseAutoencoder.pdf}

@@

\bibitem{uci}
   C.L. Blake and C.J. Merz,
   `` UCI repository of machine learning databases"
   \textbf{http://archive.ics.uci.edu/ml/datasets/}
   \textbf{Molecular+Biology+\}
   \textbf{(Protein+Secondary+Structure)}
